\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{CJKutf8}
\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\hypersetup{
     colorlinks = true,
     linkcolor = blue,
     anchorcolor = blue,
     citecolor = blue,
     filecolor = blue,
     urlcolor = BlueViolet
     }


\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\color{BlueViolet}
}{}{0em}{}[\color{Gray}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[5]{
  \item
  \begin{tabular*}{0.97\textwidth}{@{\extracolsep{\fill}}lr}
    \textbf{#1} \hspace{1pt} \textit{{\footnotesize#2}} & \small{#3} \\
    \small{#4} & \textit{\small #5}
  \end{tabular*}\vspace{-3pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
 \textbf{\Huge \begin{CJK*}{UTF8}{bsmi}黃俊城\end{CJK*}}
    &   \href{https://github.com/nopphrakornk}
    {\faicon{github-square}\ github.com/nopphrakornk}\\ 
    \href{mailto:nopphrakorn.k@gmail.com}{\faEnvelope \ nopphrakorn.k@gmail.com} &
    \href{https://www.linkedin.com/in/nopphrakorn-kerdsamut/}
    {\faLinkedinSquare \ linkedin.com/in/nopphrakorn-kerdsamut} 

\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experiences}
\resumeSubHeadingListStart
\resumeSubheading{\href{https://www.pttep.com}{\color{Black} \large{PTTEP}}}{Oil \& Gas}{Bangkok, Thailand}{Data Science Officer}{Dec '21-}
   	\resumeItemListStart
     \resumeItem{In House developments}
     {Consult, develop, deploy, support, and maintain projects from various departments.}
     \resumeItemListStart
        \resumeItem{Equipment Data Collection and Analysis}{Centralized and standardize equipment data using text models. Enabled reliability analyses aligned with Offshore \& Onshore Reliability Data (OREDA) standards.
                                                            Unified webpage for display and verification from multiple data sources.}
                                                            
        \resumeItem{PR/PO Automation}{RPA that assigns weekly Purchase Requests (PRs) to procurement officers based on their workload. 
                                      Once approved and verified by the officers,  the bot automatically generates templates to issue Purchase Orders (POs).}
        \resumeItem{Flowarm Integrity Inspection Optimization}{Enabled Data-Driven Decision Making strategy that optimized inspection intervals from corrosion data.}
        \resumeItem{Stock Duplication Detection}{Leveraged text similarity with LLM to identify and eliminate duplicate items in stock inventory.}
   	\resumeItemListEnd
    \resumeItem{Outsourced developments}{Assist and oversee outsourced projects to ensure corporate standards.}
    \resumeItem{Coporate Digital Transformation}{Deliver presentations and showcase projects to various departments 
                                                 to drive the adoption of data science technologies.}
    \resumeItem{Intership Mentor Program}{Guide and support internship students.}
  \resumeItemListEnd  

\resumeSubheading{\href{https://www.kaidee.com/en}{\color{Black}\large{Kaidee}\small{.com}}}{E-commerce}{Bangkok, Thailand}{Data Scientist}{July '20 - March '21}
	\resumeItemListStart
      	\resumeItem{Listing Page Suggestion APIs}
      	{Built pytorch models to improve user's listing experience. 
        All models are retrained weekly.}
      		\resumeItemListStart
      			\resumeItem{Vehicle Price Suggester}{Pipeline of autoencoder and multilayer perceptron model. 
            The autoencoder scores the uniqueness of a vehicle and the MLP suggests the price.}
      			\resumeItem{Category Recommender}{Convoluted neural network classifier to predict the category from listing text.}
      			\resumeItem{Price Suggester}{Convoluted neural network regressor to suggest 3 prices from listing text. 
            The model is train with quantile loss to suggest price bounds.}
   			\resumeItemListEnd
   		\resumeItem{Search Term Extraction}{Convoluted neural network that predicts the top ten search terms given listing's title and description.}
   	\resumeItemListEnd  
\resumeSubHeadingListEnd

  %--------Technical Skills------------
\section{Skills}
 \resumeSubHeadingListStart
   \resumeItem{
     \textbf{Languages}}{Python, git, Google Cloud, SQL, HTML, jQuery, css, \LaTeX}
\resumeItem{
     \textbf{Spoken Languages}}{\normalfont  $\underbrace{\textrm{Thai}}_{Native}$, $\underbrace{\textrm{English}}_{Fluent}$, $\underbrace{\textrm{Mandarin}}_{Colloquial}$}
 \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://cds.nyu.edu/}{\color{Black}New York University}}{}
      {Sept 2018 -- \textit{May 2020}}{M.Sc. in Data Science}{New York City, NY}
        \resumeItemListStart
            \resumeItem{Webpage Recommender Datathon}{Developed recommendation systems based on user interactions and website content.}
            \resumeItem{NYC Datathon}{Analyzed and identified recurring NYC's subway system issues, and developed solutions to 
                                      enhance operational efficiency and passenger experience.}
        \resumeItemListEnd
    \resumeSubheading
      {\href{https://muic.mahidol.ac.th/eng/programs/undergraduate-programs/science/major-in-physics/}{\color{Black} Mahidol University International College}}{}
      {Apr. 2014 -- Apr. 2018}{B.Sc. in Physics }{Nakhon Pathom, Thailand}
    \resumeItemListStart
      \resumeItem{Toxic Comment Classifiers}{Implemented and compared multiple models that predict comment toxicity.}
  \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}