%-------------------------
% Resume in Latex
% Author : NOPPHRAKORN KERDSAMUT
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{CJKutf8}
\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\hypersetup{
     colorlinks = true,
     linkcolor = blue,
     anchorcolor = blue,
     citecolor = blue,
     filecolor = blue,
     urlcolor = BlueViolet
     }


\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.4in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\color{BlueViolet}
}{}{0em}{}[\color{Gray}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small{#2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-1pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
 \textbf{\huge Nopphrakorn Kerdsamut \large (Nop)}
    & Email : \href{mailto:nopphrakorn.k@gmail.com}{nopphrakorn.k@gmail.com}\\
  \href{https://www.linkedin.com/in/nopphrakorn-kerdsamut/}
  {\faLinkedinSquare \ linkedin.com/in/nopphrakorn-kerdsamut} & Mobile : (+66) 8 5550 1122
  \\
    \href{https://github.com/nopphrakornk}
  {\faicon{github-square}\ github.com/nopphrakornk}
  
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Kaidee}{Bangkok, Thailand}{Data Scientist}{July 2020 - March 2021}
	\resumeItemListStart
      	\resumeItem{Post Page Suggestion API}
      	{Built and deployed an api for suggestions on the listing page. The api contains three main models: \textit{Atrributes-to-Price Regressor}, \textit{Title-to-Category Classifier} and \textit{Title-to-Price Regressor}. All models in the api are updated and retrained weekly.}
      		\resumeItemListStart
      			\resumeItem{Attribute-to-Price Regressor}{Built a pipeline of autoencoder and multilayer perceptrons models. The autoencoder scores the uniqueness of a vehicle given attributes where the multilayer perceptron suggests the price of the vehicle given encoded attributes.}
      			\resumeItem{Title-to-Category Classifier}{CNN classifier to predict the category given ad listing text. Created a more streamlined listing experience.}
      			\resumeItem{Title-to-Price Regressor}{CNN regressor to suggest 3 prices given ad listing text. The model is train with quantile loss to suggest price bounds.}
   			\resumeItemListEnd

   		\resumeItem{Search Term Extraction}{CNN model that predicts the top ten search terms given ad listing's title and description. Aim to improve SEO.}
   	\resumeItemListEnd
  \resumeSubheading{Moonlight Brunch}{New York City, NY}{Data Scientist Intern}{Summer 2019}
   	\resumeItemListStart
   		\resumeItem{News Headline Categorization}{Web scraped news headline from multiple sources and implemented a pipeline that preprocess text used for topic modeling through LDA.}
   	\resumeItemListEnd
      
     
\iffalse 
\resumeSubheading{New York Life Insurance }{New York, NY}{Capstone Project Collaboration}{Fall 2019}
	\resumeItemListStart
  		\resumeItem{Data Processing}{Web scraped competitor's agents location along with data from New York Life to create features for models. Visualize the features geographically through Geopandas.}
  		\resumeItem{Location Ranking System}{Ranked counties based on potential recruitment and clients. Trained an XGBoost on existing New York Life locations to predict recruitment and clients. Visualize the ranked counties geographically.}
 	\resumeItemListEnd
 	
\resumeSubheading{Mored\'{e}co}{Bangkok, Thailand}{Representative}{Apr 2018}
   	\resumeItemListStart
		\resumeItem{Event Coordination}{Represented the Taiwanese furniture brand in Thailand's  annual \textit{Architect and Style} expo. Successfully garnered international investors.}
   	\resumeItemListEnd
   	
\resumeSubheading{Moonlight Brunch}{New York, NY}{Data Scientist Intern}{Summer 2019}
   	\resumeItemListStart
   		\resumeItem{Data Mining}{Web scraped and organized news headline from multiple sources.}
        \resumeItem{Natural Language Processing}{Implemented a pipeline that preprocess text data and extracted necessary features with TF-IDF smoothing from unstructured text and transform into vector representations. The representation is used for topic modeling through LDA.}
\fi

\resumeSubHeadingListEnd

  %--------Technical Skills------------
\section{Technical Skills}
 \resumeSubHeadingListStart
   \resumeItem{
     \textbf{Technical}}{Python (\footnotesize{Pandas, PyTorch, Scikit-Learn, PySpark}), SQL, Hadoop, \LaTeX}
\resumeItem{
     \textbf{Languages}}{\normalfont  Thai, English, Mandarin \scriptsize (aka \begin{CJK*}{UTF8}{bsmi}黃俊城\end{CJK*})}
 \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://cds.nyu.edu/}{\color{Black}New York University}}{New York City, NY}
      {M.S. in Data Science}{Sept 2018 -- \textit{May 2020}}
        \resumeItemListStart
            \resumeItem{Coursework:}
                {Machine Learning, Big Data, Computer Vision, Time Series Analysis, NLU,  Text as Data}
        \resumeItemListEnd
    \resumeSubheading
      {\href{https://muic.mahidol.ac.th/eng/programs/undergraduate-programs/science/physics/}{\color{Black} Mahidol University International College}}{Nakhon Pathom, Thailand}
      {B.S. in Physics with Honors}{Apr. 2014 -- Apr. 2018}
      \resumeItemListStart
            \resumeItem{Exchange Program}
                {University of North Carolina at Chapel Hill (Fall 2016)}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%

 
 

%-----------PROJECTS-----------------
\section{Research and Selected Projects}
\resumeSubHeadingListStart

\resumeItem{Sales Location Prediction}{Collaborating with \textit{New York Life Insurance Company}, web scraped competitor's data in addition to public and internal dataset to predict the optimal county for a sales office. Visualize the ranked counties geographically.}   

\resumeItem{Understood.org-CDS Datathon}{Implemented recommendation systems to predict a user's next website visit. Dataset includes user's past interactions and demographics. User-based collaborative filtering and popularity with time decay methods improved precision with 3 recommendations by 7\% and 8\% from a random prediction baseline. Awarded $2^{nd}$ place at the challenge.}

\resumeItem{Music Recommendation}
      {Constructed music recommendation system through collaborative filtering based on matrix factoring approach. Fetched and processed ${\sim} 12$GB of data through \texttt{spark}. Utilized \texttt{SparkMLib}'s alternating least squares (ALS) algorithm to learn latent factors representations for users and items.}
      
\resumeItem{Enigma-CDS Datathon}
      {Exploited various datasets related to New York MTA to identify stations that are the least accessible targeted for tourists, seniors and disabled. Presented the accessibility of each station geographically. Rated the accessibility of each stations by extracting from Wi-Fi, elevator outages, station entrances, and nearby bus stop shelters dataset.}
      
   
\iffalse 
\resumeItem{Ising Model Simulation}
      {Video simulated the mathematical model that describes ferromagnetism (magnets) in typical lattice square and hexagonal configurations by applying Monte Carlo and Markov Chain algorithms. The macroscopic variables (\textit{magnetization, total energy, specific heat}) from the simulation were compared with Onsager's exact solutions.}
      
\resumeItem{\small Black Friday Sales Prediction} {Applied multiple supervised models to predict consumer's behavior on Black Friday based on prior sales. Specifically, linear regression, random forest, XGboost, Neural Network are implemented and the models were evaluated by RSME.}
\fi

\resumeSubHeadingListEnd
\end{document}